### 2022-06-06 chapters/04-chapter-4.tex
txs auto checkin

operasi \texttt{placeorder} dari \textit{service} \texttt{CheckoutService}, operasi \texttt{listrecommendations} dari \textit{service} \texttt{RecommendationService}, operasi \texttt{getproduct} dari \textit{service} \texttt{ProductCatalogService}, \texttt{listproducts} dari \textit{service} \texttt{ProductCatalogService}, dan operasi \texttt{getquote} dari \textit{service} \texttt{ShippingService}.

>>>>

operasi \texttt{placeorder} dari \textit{service} \texttt{Checkout Service}, operasi \texttt{listrecommendations} dari \textit{service} \texttt{Recommendation Service}, operasi \texttt{getproduct} dari \textit{service} \texttt{ProductCatalog Service}, \texttt{listproducts} dari \textit{service} \texttt{ProductCatalog Service}, dan operasi \texttt{getquote} dari \textit{service} \texttt{Shipping Service}.
